\documentclass{../vespers-half-sheet}
\usepackage{multicol}

\begin{document}

\chapter*{Dominica V Post Epiphaniam}

%\section*{Magnificat}

\textit{\textnormal{Cant.} My soul doth magnify the Lord: and my spirit hath rejoiced in God my Saviour.}

\gresetinitiallines{1}
\gregorioscore{magnificat-intonation}

 \begin{latinenglishsection}
\latinenglish{
	3. Quia respéxit humilitátem an\textbf{cíl}læ \textbf{su}æ:~*
		ecce enim ex hoc beátam me dicent omnes gene\textit{ra}\textit{ti}\textbf{ó}nes.
	
	4. Quia fecit mihi \textbf{ma}gna qui \textbf{pot}ens est:~*
		et sanctum \textit{no}\textit{men} \textbf{e}jus.
	
	5. Et misericórdia ejus a progénie \textbf{in} pro\textbf{gé}nies~*
		timén\textit{ti}\textit{bus} \textbf{e}um.
	
	6. Fecit poténtiam in \textbf{brá}chio \textbf{su}o:~*
		dispérsit supérbos mente \textit{cor}\textit{dis} \textbf{su}i.
	
	7. Depósuit pot\textbf{én}tes de \textbf{se}de,~*
		et exal\textit{tá}\textit{vit} \textbf{hú}miles.
	
	8. Esuriéntes im\textbf{plé}vit \textbf{bo}nis:~*
		et dívites dimí\textit{sit} \textit{in}\textbf{á}nes.
	
	9. Suscépit Israël \textbf{pú}erum \textbf{su}um,~*
		recordátus misericór\textit{di}\textit{æ} \textbf{su}æ.
	
	10. Sicut locútus est ad \textbf{pa}tres \textbf{nos}tros,~*
		Abraham et sémini e\textit{jus} \textit{in} \textbf{s\'{\ae}}cula.
	
	Glória \textbf{Pa}tri, et \textbf{Fí}lio,~*
		et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
}{	
	%1. My soul doth magnify the Lord.
	
	%2. And my spirit hath rejoiced in God my Saviour.
	
	3. Because he hath regarded the humility of his handmaid; for behold from henceforth all generations shall call me blessed.
	
	4. Because he that is mighty, hath done great things to me; and holy is his name.
	
	5. And his mercy is from generation unto generations, to them that fear him.
	
	6. He hath shewed might in his arm: he hath scattered the proud in the conceit of their heart.
	
	7. He hath put down the mighty from their seat, and hath exalted the humble.
	
	8. He hath filled the hungry with good things; and the rich he hath sent empty away.
	
	9. He hath received Israel his servant, being mindful of his mercy: 
	
	10. As he spoke to our fathers, to Abraham and to his seed for ever. 
	
	Glory be.
}

\end{latinenglishsection}

Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.

\vfill
\pagebreak

\gresetinitiallines{0}
\gregorioscore{magnificat-antiphon}

\textit{\textnormal{Ant.} Gather up first the weeds, and bind them into bundles to burn; but the wheat gather into My barns, saith the Lord.
}


\section*{Collect}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~Dómine exáudi oratiónem meam.\\
	\Rbar.~Et clamor meus ad te véniat.
	
	Orémus.
	Famíliam tuam, qu\'{\ae}sumus Dómine, contínua pietáte custódi: ut quæ in sola spe grátiæ cæléstis innítitur,
	tua semper protectióne muniátur.
	Per Dóminum.
	\Rbar.~Amen.
}{
	Lord, hear my prayer.
	\Rbar.~And let my cry come unto Thee.
	
	Let us pray.
	In thine infinite goodness, we beseech thee, O Lord, to watch over Thy household,
	that even as it relies solely upon the hope of Thy heavenly grace, so it may ever be defended by Thy protection.
	Through our Lord.
	\Rbar.~Amen.
}

\end{latinenglishsection}

\end{document}