\documentclass{../vespers-booklet}
\usepackage{multicol}

\begin{document}

\chapter*{Vespers Insert for 2 Oct 2021}

\textit{This Saturday comes before the First Sunday of October and the Nineteenth after Pentecost.}

\section*{Magnificat}

\textit{\textnormal{Ant. Magn.} May the Lord open. \textnormal{Cant.} My soul doth magnify the Lord.
And my spirit hath rejoiced in God my Saviour.}

Make the sign of the cross with the cantor at the word \textit{Magnificat}, and remain standing throughout.

\gresetinitiallines{1}
\gregorioscore{magnificat-intonation}

 \begin{latinenglishsection}

\latinenglish{	
	3. Quia respéxit humilitátem ancíllæ \textbf{su}æ:~*
		ecce enim ex hoc beátam me dicent omnes gene\textit{ra}\textit{ti}\textbf{ó}nes.
	
	4. Quia fecit mihi magna qui \textbf{pot}ens est:~* 
		et sanctum \textit{no}\textit{men} \textbf{e}jus.
		
	\pagebreak
	
	5. Et misericórdia ejus a progénie in pro\textbf{gé}nies~*
		timén\textit{ti}\textit{bus} \textbf{e}um.
	
	6. Fecit poténtiam in bráchio \textbf{su}o:~*
		dispérsit supérbos mente \textit{cor}\textit{dis} \textbf{su}i.
	
	7. Depósuit poténtes de \textbf{se}de,~*
		et exal\textit{tá}\textit{vit} \textbf{hú}miles.
	
	8. Esuriéntes implévit \textbf{bo}nis:~*
		et dívites dimí\textit{sit} \textit{in}\textbf{á}nes.
	
	9. Suscépit Israël púerum \textbf{su}um,~*
		recordátus misericór\textit{di}\textit{æ} \textbf{su}æ.
	
	10. Sicut locútus est ad patres \textbf{nos}tros,~*
		Abraham et sémini e\textit{jus} \textit{in} \textbf{s\'{\ae}}cula.
	
	\textit{(bow)} Glória Patri, et \textbf{Fí}lio,~* 
		et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
}{	
	3. Because he hath regarded the humility of his handmaid; for behold from henceforth all generations shall call me blessed.
	
	4. Because he that is mighty, hath done great things to me; and holy is his name.
	
	\pagebreak
	
	5. And his mercy is from generation unto generations, to them that fear him.
	
	6. He hath shewed might in his arm: he hath scattered the proud in the conceit of their heart.
	
	7. He hath put down the mighty from their seat, and hath exalted the humble.
	
	8. He hath filled the hungry with good things; and the rich he hath sent empty away.
	
	9. He hath received Israel his servant, being mindful of his mercy: 
	
	10. As he spoke to our fathers, to Abraham and to his seed for ever. 
	
	Glory be.
}

\end{latinenglishsection}

\textit{(rise)} Sicut erat in princípio, et nunc, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.

\textbf{Sit.}

\gresetinitiallines{0}
\gregorioscore{magnificat-antiphon}

\textit{\textnormal{Ant.} May the Lord open your hearts in His law and in His commandments, and may the Lord our God send you peace.}

\vfill

\textbf{Stand.}

\gresetinitiallines{0}
\gabcsnippet{
	(c4) <sp>V/</sp>. Dó(g)mi(h)ne(h) e(h)xáu(h)di(g) o(g)ra(g)ti(g)ó(g)nem(h) me(hg)am.(g.) (::)
	<sp>R/</sp>. Et(g) cla(h)mor(h) me(h)us(g) ad(g) te(g) vé(h)ni(h)at.(h.) (::)
}

\textit{Lord, hear my prayer. \Rbar.~And let my cry come unto Thee.}

\begin{latinenglishsection}

%\latinenglish{
%	\Vbar.~Dómine exáudi orátionem meam.\\
%	\Rbar.~Et clamor meus ad te véniat.
%}{
%	Lord, hear my prayer.
%	\Rbar.~And let my cry come unto Thee.
%}

%\flushpage

\latinenglish{
	Orémus.
	Omnípotens et miséricors Deus, univérsa nobis adversántia propitiátus exclúde:
	ut mente et córpore páriter expedíti, quæ tua sunt, líberis méntibus exsequámur.
	Per Dóminum nostrum\dots
	
	\gresetinitiallines{0}
	\gabcsnippet{
		(c4) A(g.)men.(h.) (::)
	}
}{
	Let us pray.
	O almighty and merciful God, in Thy goodness keep us, we beseech Thee, from all things hurtful;
	that we, being ready both in body and soul may acomplish those things which belong to Thy service.
	Through our Lord.
	\Rbar.~Amen.
}

\end{latinenglishsection}

\section*{Commemoration of the Holy Guardian Angels}

\textit{\textnormal{Ant.} Holy Angels, our Guardians, defend us in battle, that we may not perish in the terrible judgment.}

\textbf{Sit} at the asterisk.

\gresetinitiallines{1}
\gregorioscore{../commemorations/guardian-angels-2v}

\textbf{Stand.}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~In conspéctu Angelórum psallam tibi Deus meus.\\
	\Rbar.~Adorábo ad templum sanctum tuum, et confitébor nómini tuo.
	
	Orémus.
	Deus, qui ineffábili providéntia sanctos Angelos tuos ad nostram custódiam míttere dignáris:
largíre supplícibus tuis; et eórum semper protectióne deféndi, et ætérna societáte gaudére.
}{
	In the sight of the Angels I will sing unto Thee, O my God.
	\Rbar.~I will worship at Thy holy temple, and give praise to Thy Name.
	
	Let us pray.
	O God, Who in Thine ineffable providence hast deigned to send Thy holy Angels to watch over us,
	grant to Thy suppliants always to find safety in their protection and in eternity to share their happiness.
}

\end{latinenglishsection}

\section*{Commemoration of St. Therese of the Child Jesus}

\textit{\textnormal{Ant.} Come, Spouse of Christ, receive the crown which the Lord hath prepared for thee for all eternity.}

\textbf{Sit} at the asterisk.

\gresetinitiallines{1}
\gregorioscore{../commemorations/virgin-1v}

\textbf{Stand.}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~Spécia tua et pulchritúdine tua.\\
	\Rbar.~Inténde, próspere procéde, et regna.
}{
	In thy glory and thy splendor.
	\Rbar.~Go forth, advance with victory and reign.
}

\latinenglish{
	Orémus.
	Dómine, qui dixisti: Nisi efficiámini sicut párvuli, non intrábitis in regnum c{\oe}lórum:
	da nobis, qu\'{\ae}sumus: ita sanctæ Terésiæ Vírginis in humilitáte et simplicitáte cordis vestígia sectári,
	ut præmia consequámur ætérna.
	Qui vivis et regnas cum Deo Patre in unitáte Spíritus Sancti Deus,
}{
	Let us pray.
	O Lord, Who hast said: Unless ye become as little children ye shall not enter into the kingdom of heaven:
	grant us, we beseech Thee, so to follow in humility and simplicity of heart, the footsteps of the virgin St. Teresa,
	that we may obtain everlasting reward.
	Who livest and reignest.
}

\end{latinenglishsection}

\gresetinitiallines{0}
\gabcsnippet{
	(c4) Per(g) óm(h)ni(h)a(h) s<sp>'ae</sp>(h)cu(h)la(h) sæ(g)cu(h)ló(hg)rum.(g.) <sp>R/</sp>.(::) A(g.)men.(h.) (::)
	<sp>V/</sp>. Dó(g)mi(h)ne(h) e(h)xáu(h)di(g) o(g)ra(g)ti(g)ó(g)nem(h) me(hg)am.(g.) (::)
	<sp>R/</sp>. Et(g) cla(h)mor(h) me(h)us(g) ad(g) te(g) vé(h)ni(h)at.(h.) (::)
}

\textit{Lord, hear my prayer. \Rbar.~And let my cry come unto Thee.}

\textit{Continue from \textnormal{Benedicamus Domino} in the main booklet. The Marian anthem at the end of the Office
is \textnormal{Salve Regina}, simple tone, no. 224 in the \textnormal{Traditional Roman Hymnal}.}


\end{document}