\documentclass{../vespers-booklet}
\usepackage{multicol}

\begin{document}

\chapter*{Vespers on Saturday}

\vfill

\textit{Before the Office, all kneel for some time in silent prayer.
All then stand and say silently one \textnormal{Pater noster} (Our Father)
and \textnormal{Ave Maria} (Hail Mary). Then make the sign of the cross with the leader
as he intones:}

 \gresetinitiallines{1}
\gregorioscore{../common/deus-in-adjutorium}

\textit{After Septuagesima Sunday until Easter, \textnormal{Alleluia} is replaced  with}

\gresetinitiallines{0}
\gabcsnippet{
	(c3) Laus(h) ti(h)bi(h) Dó(h)mi(h)ne(h'_) Rex(h) æ(h)tér(h)næ(i) gló(h')ri(h)æ.(g.) (::)
}

\textit{
O God, come to my assistance.
\Vbar.~O Lord, make haste to help me.
Glory be to the Father, and to the Son, and to the Holy Spirit,
as it was in the beginning, is now, and ever shall be, world without end. Amen.
Alleluia. \textnormal{Or:} Praise to Thee, O Lord, King of endless glory.}

\pagebreak

\section*{Psalm 143}

\textit{\textnormal{Ant. 1.} Blessed\dots \textnormal{Ps.} be the Lord my God, who teacheth my hands to fight, and my fingers to war.}

Stand until the asterisk halfway through the first verse, then sit.

\gresetinitiallines{1}
\gregorioscore{ps143-intonation}

 \begin{latinenglishsection}

\latinenglish{

	2. Misericórdia mea, et refúgi\textit{um} \textbf{me}um:~*
		suscéptor meus, et libe\textit{rá}\textit{tor} \textbf{me}us:
	
	3. Protéctor meus, et in ipso \textit{spe}\textbf{rá}vi:~*
		qui subdit pópulum \textit{me}\textit{um} \textbf{sub} me.
	
	4. Dómine, quid est homo quia innotuís\textit{ti} \textbf{e}i?~*
		aut fílius hóminis, quia ré\textit{pu}\textit{tas} \textbf{e}um?
	
	5. Homo vanitáti sími\textit{lis} \textbf{fac}tus est:~*
		dies ejus sicut um\textit{bra} \textit{præ}\textbf{tér}\-eunt.
	
	6. Dómine, inclína cælos tuos, et \textit{de}\textbf{scén}de:~*
		tange montes, et \textit{fu}\textit{mi}\textbf{gá}bunt.
	
	7. Fúlgura coruscatiónem, et dissipá\textit{bis} \textbf{e}os:~*
		emítte sagíttas tuas, et contur\textit{bá}\textit{bis} \textbf{e}os.
		
	\pagebreak
	
	8. Emítte manum tuam de alto,~\GreDagger\
		éripe me, et líbera me de a\textit{quis} \textbf{mul}tis:~*
		de manu filiórum a\textit{li}\textit{e}\textbf{nó}rum.
	
	9. Quorum os locútum est va\textit{ni}\textbf{tá}tem:~*
		et déxtera eórum, déxtera in\textit{i}\textit{qui}\textbf{tá}tis.
	
	10. Deus, cánticum novum cantá\textit{bo} \textbf{ti}bi:~*
		in psaltério, decachórdo \textit{psal}\textit{lam} \textbf{ti}bi.
	
	11. Qui das salú\textit{tem} \textbf{ré}gibus:~*
		qui redemísti David, servum tuum, de gládio malígno: \textit{é}\textit{ri}\textbf{pe} me.
	
	12. Et érue me de manu filiórum alienórum,~\GreDagger
		quorum os locútum est va\textit{ni}\textbf{tá}tem:~*
		et déxtera eórum, déxtera in\textit{i}\textit{qui}\textbf{tá}tis.
	
	13. Quorum fílii, sicut novéllæ planta\textit{ti}\textbf{ó}nes~*
		in juven\textit{tú}\textit{te} \textbf{su}a.
	
	14. Fíliæ eórum \textit{com}\textbf{pó}sitæ:~*
		circumornátæ ut simili\textit{tú}\textit{do} \textbf{tem}pli.
	
	15. Promptuária eó\textit{rum} \textbf{ple}na:~*
		eructántia ex \textit{hoc} \textit{in} \textbf{il}lud.
	
	16. Oves eórum f{\oe}tósæ, abundántes in egréssi\textit{bus} \textbf{su}is:~*
		boves e\textit{ó}\textit{rum} \textbf{cras}sæ.
	
}{
	 2. My mercy, and my refuge: my support, and my deliverer.
	 
	 3. My protector, and I have hoped in him: who subdueth my people under me. 
	 
	 4. Lord, what is man, that thou art made known to him? or the son of man, that thou makest account of him? 
	 
	 5. Man is like to vanity: his days pass away like a shadow. 
	 
	 6. Lord, bow down thy heavens and descend: touch the mountains and they shall smoke.
	
	7. Send forth lightning, and thou shalt scatter them:
	shoot out thy arrows, and thou shalt trouble them.
	
	8. Put forth thy hand from on high, take me out, and deliver me from many waters:
	from the hand of strange children. 
	
	9. Whose mouth hath spoken vanity: and their right hand is the right hand of iniquity.
	
	\pagebreak
	
	10. To thee, O God, I will sing a new canticle: on the psaltery and an instrument of ten strings I will sing praises to thee. 
	
	11. Who givest salvation to kings: who hast redeemed thy servant David from the malicious sword: Deliver me.
	
	12. And rescue me out of the hand of strange children; whose mouth hath spoken vanity:
	and their right hand is the right hand of iniquity.
	
	 13. Whose sons are as new plants in their youth.
	 
	 14. Their daughters decked out, adorned round about after the similitude of a temple. 
	 
	 15. Their storehouses full, flowing out of this into that.
	 
	 16. Their sheep fruitful in young, abounding in their goings forth: their oxen fat.
	 
	 17. There is no breach of wall, nor passage, nor crying out in their streets. 
	 
	 18. They have called the people happy, that hath these things: but happy is that people whose God is the Lord. 
	
	Glory be.
}

\end{latinenglishsection}

17. Non est ruína macériæ, ne\textit{que} \textbf{tráns}itus:~*
	neque clamor in platé\textit{is} \textit{e}\textbf{ó}rum.

18. Beátum dixérunt pópulum, cu\textit{i} \textbf{hæc} sunt:~*
	beátus pópulus, cujus Dóminus \textit{De}\textit{us} \textbf{e}jus.

\textit{(bow)} Glória Patri, \textit{et} \textbf{Fí}lio,~*
	et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.

\textit{(rise)} Sicut erat in princípio, et nunc, \textit{et} \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.

\gresetinitiallines{0}
\gregorioscore{ps143-antiphon}
\textit{\textnormal{Ant.} Blessed be the Lord my God.}

\section*{Psalm 144}

\textit{\textnormal{Ant. 2.} Every day. \textnormal{Ps.} I will extol thee, O God my king: and I will bless thy name for ever; yea, for ever and ever.}

Stand until the asterisk halfway through the first verse, then sit.

\gresetinitiallines{1}
\gregorioscore{ps144-intonation}

 \begin{latinenglishsection}

\latinenglish{
	2. Per síngulos dies benedícam \textbf{ti}bi:~*
		et laudábo nomen tuum in s\'{\ae}culum, et in s\'{\ae}\textit{cu}\textit{lum} \textbf{s\'{\ae}}culi.
	
	3. Magnus Dóminus, et laudábilis \textbf{ni}mis:~*
		et magnitúdinis ejus \textit{non} \textit{est} \textbf{fi}nis.
	
	4. Generátio et generátio laudábit ópera \textbf{tu}a:~*
		et poténtiam tuam pro\textit{nun}\textit{ti}\textbf{á}bunt.
	
	5. Magnificéntiam glóriæ sanctitátis tuæ lo\textbf{quén}tur:~*
		et mirabília tu\textit{a} \textit{nar}\textbf{rá}bunt.
	
	6. Et virtútem terribílium tuórum \textbf{di}cent:~*
		et magnitúdinem tu\textit{am} \textit{nar}\textbf{rá}bunt.
	
	7. Memóriam abundántiæ suavitátis tuæ eruc\textbf{tá}bunt:~*
		et justítia tua \textit{ex}\textit{sul}\textbf{tá}bunt.
	
	8. Miserátor, et miséricors \textbf{Dó}mi\-nus:~*
		pátiens, et mul\textit{tum} \textit{mi}\textbf{sé}ricors.
	
	9. Suávis Dóminus uni\textbf{vér}sis:~*
		et miseratiónes ejus super ómnia ó\textit{pe}\textit{ra} \textbf{e}jus.
	
	10. Confiteántur tibi, Dómine, ómnia ópera \textbf{tu}a:~*
		et sancti tui bene\textit{dí}\textit{cant} \textbf{ti}bi.
	
	11. Glóriam regni tui \textbf{di}cent:~*
		et poténtiam tu\textit{am} \textit{lo}\textbf{quén}tur:
	
	12. Ut notam fáciant fíliis hóminum poténtiam \textbf{tu}am:~*
		et glóriam magnificéntiæ \textit{re}\textit{gni} \textbf{tu}i.
	
	13. Regnum tuum regnum ómnium sæcu\textbf{ló}rum:~*
		et dominátio tua in omni generatióne et gene\textit{ra}\textit{ti}\textbf{ó}nem.
	
	14. Fidélis Dóminus in ómnibus verbis \textbf{su}is:~*
		et sanctus in ómnibus opé\textit{ri}\textit{bus} \textbf{su}is.
	
	15. Allevat Dóminus omnes qui \textbf{cór}ruunt:~*
		et érigit om\textit{nes} \textit{e}\textbf{lí}sos.
	
	16. Oculi ómnium in te sperant, \textbf{Dó}mine:~*
		et tu das escam illórum in témpore \textit{op}\textit{por}\textbf{tú}no.
	
	17. Aperis tu manum \textbf{tu}am:~*
		et imples omne ánimal bene\textit{dic}\textit{ti}\textbf{ó}ne.
	
	18. Justus Dóminus in ómnibus viis \textbf{su}is:~*
		et sanctus in ómnibus opé\textit{ri}\textit{bus} \textbf{su}is.
	
	19. Prope est Dóminus ómnibus invocántibus \textbf{e}um:~*
		ómnibus invocántibus eum in \textit{ve}\textit{ri}\textbf{tá}te.
	
	20. Voluntátem timéntium se fáciet:~\GreDagger\
		et deprecatiónem eórum ex\textbf{áu}diet:~*
		et salvos fá\textit{ci}\textit{et} \textbf{e}os.
}{
	 2. Every day I will bless thee: and I will praise thy name for ever; yea, for ever and ever.
	 	
	 3. Great is the Lord, and greatly to be praised: and of his greatness there is no end.
	 	
	 4. Generation and generation shall praise thy works: and they shall declare thy power.
	 	
	 5. They shall speak of the magnificence of the glory of thy holiness: and shall tell thy wondrous works.
	
	6. And they shall speak of the might of thy terrible acts: and shall declare thy greatness.
	
	7. They shall publish the memory of the abundance of thy sweetness: and shall rejoice in thy justice.
	
	8. The Lord is gracious and merciful: patient and plenteous in mercy.
	
	\pagebreak
	
	9. The Lord is sweet to all: and his tender mercies are over all his works.
	
	10. Let all thy works, O lord, praise thee: and let thy saints bless thee.
	
	11. They shall speak of the glory of thy kingdom: and shall tell of thy power.
	
	12. To make thy might known to the sons of men: and the glory of the magnificence of thy kingdom.
	
	13. Thy kingdom is a kingdom of all ages: and thy dominion endureth throughout all generations.
	
	14. The Lord is faithful in all his words: and holy in all his works.
	
	15. The Lord lifteth up all that fall: and setteth up all that are cast down.
	
	16. The eyes of all hope in thee, O Lord: and thou givest them meat in due season.
	
	17. Thou openest thy hand, and fillest with blessing every living creature.
	
	18. The Lord is just in all his ways: and holy in all his works.
	
	19. The Lord is nigh unto all them that call upon him: to all that call upon him in truth.
	
	20. He will do the will of them that fear him: and he will hear their prayer, and save them.
	
	21. The Lord keepeth all them that love him; but all the wicked he will destroy.
	
	22. My mouth shall speak the praise of the Lord: and let all flesh bless thy holy name for ever; yea, for ever and ever. 
	
	Glory be.
}

\end{latinenglishsection}

21. Custódit Dóminus omnes dili\textbf{gén}tes se:~*
	et omnes peccató\textit{res} \textit{dis}\textbf{pér}det.

22. Laudatiónem Dómini loquétur os \textbf{me}um:~*
	et benedícat omnis caro nómini sancto ejus in s\'{\ae}culum, et in s\'{\ae}\textit{cu}\textit{lum} \textbf{s\'{\ae}}culi.
	
\vfill
	
\pagebreak

%\textit{(bow)} Glória Patri, et \textbf{Fí}lio,~*
%	et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
%
%\textit{(rise)} Sicut erat in princípio, et nunc, et \textbf{sem}per,~*
%	et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.

\gresetinitiallines{0}
\gregorioscore{ps144-antiphon-with-verses}
\textit{\textnormal{Ant.} Every day I will bless thee, O Lord.}

\section*{Psalm 145}

\textit{\textnormal{Ant. 3.} I will praise. \textnormal{Ps.} Praise the Lord, O my soul, in my life I will praise the Lord: I will sing to my God as long as I shall be.}

Stand until the asterisk halfway through the first verse, then sit.

\gresetinitiallines{1}
\gregorioscore{ps145-intonation}

 \begin{latinenglishsection}

\latinenglish{
	2. Nolíte confídere \textit{in} \textit{prin}\textbf{cí}pibus:~*
		in fíliis hóminum, in qui\textit{bus} \textit{non} \textit{est} \textbf{sa}lus.
	
	3. Exíbit spíritus ejus, et revertétur in \textit{ter}\textit{ram} \textbf{su}am:~*
		in illa die períbunt omnes cogitati\textit{ó}\textit{nes} \textit{e}\textbf{ó}rum.
	
	4. Beátus, cujus Deus Jacob adjútor ejus,~\GreDagger\
		spes ejus in Dómino De\textit{o} \textit{ip}\textbf{sí}us:~*
		qui fecit cælum et terram, mare et ómni\textit{a}, \textit{quæ} \textit{in} \textbf{e}\textbf{is} sunt.
	
	5. Qui custódit veritátem in s\'{\ae}cu\-lum,~\GreDagger\
		facit judícium injúriam \textit{pa}\textit{ti}\-\textbf{én}tibus:~*
		dat escam \textit{e}\textit{su}\textit{ri}\textbf{én}\textbf{ti}bus.
	
	6. Dóminus solvit \textit{com}\textit{pe}\textbf{dí}tos:~*
		Dóminus il\textit{lú}\textit{mi}\textit{nat} \textbf{cæ}cos.
	
	7. Dóminus éri\textit{git} \textit{e}\textbf{lí}sos:~*
		Dóminus \textit{dí}\textit{li}\textit{git} \textbf{jus}tos.
	
	8. Dóminus custódit ádvenas,~\GreDagger\
		pupíllum et vídu\textit{am} \textit{su}\textbf{scí}piet:~*
		et vias pecca\textit{tó}\textit{rum} \textit{dis}\textbf{pér}det.
	
	9. Regnábit Dóminus in s\'{\ae}cula, Deus \textit{tu}\textit{us}, \textbf{Si}on,~*
		in generatiónem et ge\textit{ne}\textit{ra}\textit{ti}\textbf{ó}nem.

}{
	2. Put not your trust in princes: in the children of men, in whom there is no salvation.
	
	3. His spirit shall go forth, and he shall return into his earth: in that day all their thoughts shall perish.
	
	\pagebreak
	
	4. Blessed is he who hath the God of Jacob for his helper, whose hope is in the Lord his God: who made heaven and earth, the sea, and all things that are in them.
	
	5. Who keepeth truth for ever: who executeth judgment for them that suffer wrong: who giveth food to the hungry.
	
	6. The Lord looseth them that are fettered: the Lord enlighteneth the blind.
	
	7. The Lord lifteth up them that are cast down: the Lord loveth the just.
	
	8. The Lord keepeth the strangers, he will support the fatherless and the widow: and the ways of sinners he will destroy.
	
	9. The Lord shall reign for ever: thy God, O Sion, unto generation and generation. 

	Glory be.
}

\end{latinenglishsection}

\textit{(bow)} Glória Pa\textit{tri}, \textit{et} \textbf{Fí}lio,~*
	et Spi\textit{rí}\textit{tu}\textit{i} \textbf{Sanc}to.

\textit{(rise)} Sicut erat in princípio, et \textit{nunc}, \textit{et} \textbf{sem}per,~*
	et in s\'{\ae}cula sæ\textit{cu}\textit{ló}\textit{rum}. \textbf{A}men.

\gresetinitiallines{0}
\gregorioscore{ps145-antiphon}
\textit{\textnormal{Ant.} I will praise the Lord in my life.}

\vfill

\pagebreak

\section*{Psalm 146}

\textit{\textnormal{Ant. 4.} To our God. \textnormal{Ps.} Praise ye the Lord, because psalm is good: to our God be joyful and comely praise.}

Stand until the asterisk halfway through the first verse, then sit.

\gresetinitiallines{1}
\gregorioscore{ps146-intonation}

 \begin{latinenglishsection}

\latinenglish{
	2. Ædíficans Jerúsalem \textbf{Dó}minus:~*
		dispersiónes Israélis \textit{con}\textit{gre}\textbf{gá}bit.
	
	3. Qui sanat contrítos \textbf{cor}de:~*
		et álligat contritió\textit{nes} \textit{e}\textbf{ó}rum.
	
	4. Qui númerat multitúdinem stel\textbf{lá}rum:~*
		et ómnibus eis nó\textit{mi}\textit{na} \textbf{vo}cat.
	
	5. Magnus Dóminus noster, et magna virtus \textbf{e}jus:~*
		et sapiéntiæ ejus \textit{non} \textit{est} \textbf{nú}merus.
	
	6. Suscípiens mansuétos \textbf{Dó}minus:~*
		humílians autem peccatóres us\textit{que} \textit{ad} \textbf{ter}ram.
	
	7. Præcínite Dómino in confessi\textbf{ó}ne:~*
		psállite Deo nos\textit{tro} \textit{in} \textbf{cí}thara.
	
	8. Qui óperit cælum \textbf{nú}bibus:~*
		et parat \textit{ter}\textit{ræ} \textbf{plú}viam.
	
	9. Qui prodúcit in móntibus \textbf{fe}num: *
		et herbam servi\textit{tú}\textit{ti} \textbf{hó}minum.
	
	10. Qui dat juméntis escam ip\textbf{só}\-rum:~*
		et pullis corvórum invocán\textit{ti}\textit{bus} \textbf{e}um.
	
	11. Non in fortitúdine equi voluntátem ha\textbf{bé}bit:~*
		nec in tíbiis viri beneplácitum \textit{e}\textit{rit} \textbf{e}i.
	
	12. Beneplácitum est Dómino super timéntes \textbf{e}um:~*
		et in eis, qui sperant super misericór\textit{di}\textit{a} \textbf{e}jus.
}{
	2. The Lord buildeth up Jerusalem: he will gather together the dispersed of Israel.
	
	3. Who healeth the broken of heart, and bindeth up their bruises.
	
	4. Who telleth the number of the stars: and calleth them all by their names.
	
	5. Great is our Lord, and great is his power: and of his wisdom there is no number.
	
	6. The Lord lifteth up the meek, and bringeth the wicked down even to the ground.
	
	7. Sing ye to the Lord with praise: sing to our God upon the harp.
	
	8. Who covereth the heaven with clouds, and prepareth rain for the earth.
	
	9. Who maketh grass to grow on the mountains, and herbs for the service of men.
	
	10. Who giveth to beasts their food: and to the young ravens that call upon him.
	
	11. He shall not delight in the strength of the horse: nor take pleasure in the legs of a man.
	
	12. The Lord taketh pleasure in them that fear him: and in them that hope in his mercy. 
	
	Glory be.
}

\end{latinenglishsection}

\textit{(bow)} Glória Patri, et \textbf{Fí}lio,~*
		et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
	
\textit{(rise)} Sicut erat in princípio, et nunc, et \textbf{sem}per,~*
		et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.

\gresetinitiallines{0}
\gregorioscore{ps146-antiphon}
\textit{\textnormal{Ant.} To our God be joyful praise.}

\section*{Psalm 147}

\textit{\textnormal{Ant. 5.} Praise\dots \textnormal{Ps.} the Lord, O Jerusalem: praise thy God, O Sion.}

Stand until the asterisk halfway through the first verse, then sit.

\gresetinitiallines{1}
\gregorioscore{ps147-intonation}

 \begin{latinenglishsection}

\latinenglish{
	2. Quóniam confortávit seras por\textbf{tá}\-rum tu\textbf{á}rum:~*
		benedíxit fíliis \textit{tu}\textit{is} \textbf{in} te.
	
	3. Qui pósuit fines \textbf{tu}os \textbf{pa}cem:~*
		et ádipe fruménti \textit{sá}\textit{ti}\textbf{at} te.
	
	4. Qui emíttit elóquium \textbf{su}um \textbf{ter}ræ:~*
		velóciter currit \textit{ser}\textit{mo} \textbf{e}jus.
	
	5. Qui dat nivem \textbf{sic}ut \textbf{la}nam:~*
		nébulam sicut cí\textit{ne}\textit{rem} \textbf{spar}git.
}{
	2. Because he hath strengthened the bolts of thy gates, he hath blessed thy children within thee.
	
	3. Who hath placed peace in thy borders: and filleth thee with the fat of corn.
	
	4. Who sendeth forth his speech to the earth: his word runneth swiftly.
	
	5. Who giveth snow like wool: scattereth mists like ashes.
}

 \end{latinenglishsection}
 
 \pagebreak

\gresetinitiallines{0}
\gabcsnippet{
6. Mit(h)tit(h) crys(h)tál(h)lum(h) su(h)am(h) <b>sic</b>(ixi)ut(h) buc(h)<b>cél</b>(g)las:(h.) *(:) an(h)te(h) fá(h)ci(h)em(h) frí(h)go(h)ris(h) e(h)jus(h) quis(h) <i>sus</i>(g)<i>ti</i>(f)<b>né</b>(g)bit?(g.) (::)
}

 \begin{latinenglishsection}
 
\latinenglish{
%	6. Mittit crystállum suam \textbf{sic}ut buc\textbf{cél}las:~*
%		ante fáciem frígoris ejus quis \textit{sus}\textit{ti}\textbf{né}bit?
	
	7. Emíttet verbum suum, et lique\textbf{fá}ciet \textbf{e}a:~*
		flabit spíritus ejus, et \textit{flu}\textit{ent} \textbf{a}quæ.
	
	8. Qui annúntiat verbum \textbf{su}um \textbf{Ja}cob:~*
		justítias, et judícia \textit{su}\textit{a} \textbf{Is}raël.
	
	9. Non fecit táliter omni \textbf{na}ti\textbf{ó}ni:~*
		et judícia sua non manifes\textit{tá}\textit{vit} \textbf{e}is.
	
	\textit{(bow)} Glória \textbf{Pa}tri, et \textbf{Fí}lio,~*
		et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
		
	\textit{(rise)} Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
		et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
}{
	
	6. He sendeth his crystal like morsels: who shall stand before the face of his cold?
	
	7. He shall send out his word, and shall melt them: his wind shall blow, and the waters shall run.
	
	8. Who declareth his word to Jacob: his justices and his judgments to Israel.
	
	9. He hath not done in like manner to every nation: and his judgments he hath not made manifest to them.
	
	Glory be.
}

\end{latinenglishsection}


\gresetinitiallines{0}
\gregorioscore{ps147-antiphon}
\textit{\textnormal{Ant.} Praise the Lord, O Jerusalem.}

\section*{Little Chapter (Romans 13:11)}

\textit{All stand as the leader chants:}

O altitúdo divitiárum sapiéntiæ et sciéntiæ Dei:~\GreDagger\
quam incomprehensibília sunt judícia ejus,~*
et investigábiles viæ ejus.
\Rbar.~Deo grátias.
	
\textit{O the depth of the riches of the wisdom and of the knowledge of God!
 How incomprehensible are his judgments, and how unsearchable his ways!
 \Rbar.~Thanks be to God.}
 
 \vfill

\section*{Hymn}

\gresetinitiallines{1}
\gregorioscore{../hymns/o-lux-beata-trinitas}

{\itshape
	1. O Trinity of blessed Light,
	O Unity of sovereign might,
	as now the fiery sun departs,
	shed Thou Thy beams within our hearts.
	
	2. To Thee our morning song of praise,
	to Thee our evening prayer we raise;
	Thee may our glory evermore
	in lowly reverence adore.
	
	3. All laud to God the Father be;
	all praise, Eternal Son, to Thee;
	all glory, as is ever meet,
	to God the Holy Paraclete.
}

\vfill

\pagebreak

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>V/</sp>. Ves(h)per(h)tí(h)na(h) o(h)rá(h)ti(h)o(h) as(h)cén(h)dat(h) ad(h) te(h) Dó(h)mi(h)ne.(g'_/hvGF'E/fgf.) (::)
}

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>R/</sp>. Et(h) des(h)cén(h)dat(h) su(h)per(h) nos(h) mi(h)se(h)ri(h)cór(h)di(h)a(h) tu(h)a.(g'_/hvGF'E/fgf.) (::)
}

\textit{\Vbar.~May our evening prayer ascend to Thee, O Lord.
\Rbar.~And may Thy mercy descend upon us.}

\section*{Magnificat, Collect, and Commemorations}

This section of the Office changes each week and is found in today's insert.

\section*{Conclusion}

\textit{\Vbar.~Let us bless the Lord. \Rbar.~Thanks be to God.}

\gresetinitiallines{0}
\gregorioscore{../common/benedicamus-sunday}

\begin{latinenglishsection}

\latinenglish{
	\Vbar. Fidélium ánimæ, per misericórdiam Dei, requiéscant in pace. \\
	\Rbar. Amen.
}{
	May the souls of the faithful departed, through the mercy of God, rest in peace. \Rbar.~Amen.
}

\latinenglish{
	Pater noster \textit{(silently)}.
}{
	Our Father\dots
}

\rubric{If no other service follows:}

\latinenglish{
	\Vbar. Dóminus det nobis suam pacem. \\
	\Rbar. Et vitam ætérnam. Amen.
}{
	May the Lord grant us his peace. \Rbar.~And life eternal. Amen.
}

\rubric{Then follows the seasonal Marian anthem, found in the \textnormal{Traditional Roman Hymnal}
as noted at the end of the insert for today.}

\latinenglish{
	\Vbar. Divínum auxílium máneat semper nobíscum.\\
	\Rbar. Amen.
}{
	May the divine assistance remain with us always. \Rbar.~Amen.
}

\end{latinenglishsection}

\end{document}