%1.  Blessed be the Lord my God, who teacheth my hands to fight, and my fingers to war.
 
 2. My mercy, and my refuge: my support, and my deliverer.
 
 3. My protector, and I have hoped in him: who subdueth my people under me. 
 
 4. Lord, what is man, that thou art made known to him? or the son of man, that thou makest account of him? 
 
 5. Man is like to vanity: his days pass away like a shadow. 
 
 6. Lord, bow down thy heavens and descend: touch the mountains and they shall smoke.

7. Send forth lightning, and thou shalt scatter them:
shoot out thy arrows, and thou shalt trouble them.

8. Put forth thy hand from on high, take me out, and deliver me from many waters:
from the hand of strange children. 

9. Whose mouth hath spoken vanity: and their right hand is the right hand of iniquity. 

10. To thee, O God, I will sing a new canticle: on the psaltery and an instrument of ten strings I will sing praises to thee. 

11. Who givest salvation to kings: who hast redeemed thy servant David from the malicious sword: Deliver me.

12. And rescue me out of the hand of strange children; whose mouth hath spoken vanity:
and their right hand is the right hand of iniquity.

 13. Whose sons are as new plants in their youth.
 
 14. Their daughters decked out, adorned round about after the similitude of a temple. 
 
 15. Their storehouses full, flowing out of this into that.
 
 16. Their sheep fruitful in young, abounding in their goings forth: their oxen fat.
 
 17. There is no breach of wall, nor passage, nor crying out in their streets. 
 
 18. They have called the people happy, that hath these things: but happy is that people whose God is the Lord. 

Glory be.