\documentclass{../vespers-booklet}
\usepackage{multicol}

\begin{document}

\chapter*{Vespers of the First Sunday in Advent}

\vfill
 
 \gresetinitiallines{1}
\gregorioscore{../common/deus-in-adjutorium}

\textit{
O God, come to my assistance.
\Vbar.~O Lord, make haste to help me.
Glory be to the Father, and to the Son, and to the Holy Spirit,
as it was in the beginning, is now, and ever shall be, world without end. Amen.
Alleluia.}

\pagebreak

\section*{Psalm 109}

\textit{\textnormal{Ant. 1.} In that day. \textnormal{Ps.} The Lord said to my Lord: Sit thou at my right hand.}

\gresetinitiallines{1}
\gregorioscore{ps109-intonation}

\input{../psalms/ps109-8G}

\gresetinitiallines{0}
\gregorioscore{ps109-antiphon}
\textit{\textnormal{Ant.} In that day the mountains shall drop down sweetness, and the hills shall flow with milk and honey, alleluia.}

\section*{Psalm 110}

\textit{\textnormal{Ant. 2.} Be glad. \textnormal{Ps.} I will praise thee, O Lord, with my whole heart; in the council of the just: and in the congregation.}

\gresetinitiallines{1}
\gregorioscore{ps110-intonation}

\input{../psalms/ps110-8G}

\gresetinitiallines{0}
\gregorioscore{ps110-antiphon}
\textit{\textnormal{Ant.} Be glad, O daughter of Sion, and rejoice exceedingly, O daughter of Jerusalem, alleluia.}

\section*{Psalm 111}

\textit{\textnormal{Ant. 3.} Behold, the Lord shall come. \textnormal{Ps.} Blessed is the man that feareth the Lord: he shall delight exceedingly in his commandments.}

\gresetinitiallines{1}
\gregorioscore{ps111-intonation}

\input{../psalms/ps111-5a}

\vfill
\pagebreak

\gresetinitiallines{0}
\gregorioscore{ps111-antiphon}
\textit{\textnormal{Ant.} Behold, the Lord shall come, and all His Saints with Him: and there shall be a great light in that day, alleluia.}

\section*{Psalm 112}

\textit{\textnormal{Ant. 4.} All ye. \textnormal{Ps.} Praise the Lord, ye children: praise ye the name of the Lord.}

\gresetinitiallines{1}
\gregorioscore{ps112-intonation}

%\input{../psalms/ps112-7c}
 \begin{latinenglishsection}

\latinenglish{
	
	 2. Sit nomen Dómini \textbf{be}ne\textbf{díc}tum,~*
		ex hoc nunc, et \textbf{us}que in \textbf{s\'{\ae}}culum.
	
	 3. A solis ortu usque \textbf{ad} oc\textbf{cá}sum,~*
		laudábile \textbf{no}men \textbf{Dó}mini.
	
	 4. Excélsus super omnes \textbf{gen}tes \textbf{Dó}\-minus,~*
		et super cælos \textbf{gló}ria \textbf{e}jus.
	
	 5. Quis sicut Dóminus, Deus noster, qui in \textbf{al}tis \textbf{há}bitat,~*
		et humília réspicit in cælo \textbf{et} in \textbf{ter}ra?
	
	 6. Súscitans a \textbf{ter}ra \textbf{ín}opem,~*
		et de stércore \textbf{é}rigens \textbf{páu}perem:
	
	 7. Ut cóllocet eum \textbf{cum} prin\textbf{cí}pi\-bus,~*
		cum princípibus \textbf{pó}puli \textbf{su}i.
		
	\pagebreak
	
	 8. Qui habitáre facit stéri\textbf{lem} in \textbf{do}\-mo,~*
		matrem fili\textbf{ó}rum læ\textbf{tán}tem.
		
	Glória \textbf{Pa}tri, et \textbf{Fí}lio,~*
		et Spi\textbf{rí}tui \textbf{Sanc}to.
	

}{
 	\input{../psalms/english/ps112}
}

\end{latinenglishsection}

 Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textbf{ló}rum. \textbf{A}men.

\gresetinitiallines{0}
\gregorioscore{ps112-antiphon}
\textit{\textnormal{Ant.} All ye that thirst, come to the waters; seek the Lord while He may be found, alleluia.}

\section*{Psalm 113}

\textit{\textnormal{Ant. 5.} Behold, he shall come. \textnormal{Ps.} When Israel went out of Egypt, the house of Jacob from a barbarous people.}

\gresetinitiallines{1}
\gregorioscore{ps113-intonation}

%\input{../psalms/ps113-4A}

 \begin{latinenglishsection}

\latinenglish{	
	 2. Facta est Jud\'{\ae}a sanctificá\textit{ti}\textit{o} \textbf{e}jus,~*
		Israël \textit{pot}\textit{és}\textit{tas} \textbf{e}jus.
	
	 3. Mare vi\textit{dit}, \textit{et} \textbf{fu}git:~*
		Jordánis convér\textit{sus} \textit{est} \textit{re}\textbf{trór}sum.
	
	 4. Montes exsultavérunt \textit{ut} \textit{a}\textbf{rí}etes,~*
		et colles sic\textit{ut} \textit{a}\textit{gni} \textbf{ó}vium.
		
	\pagebreak
	
	 5. Quid est tibi, mare, \textit{quod} \textit{fu}\textbf{gís}ti:~*
		et tu, Jordánis, quia convér\textit{sus} \textit{es} \textit{re}\textbf{trór}sum?
	
	 6. Montes, exsultástis sic\textit{ut} \textit{a}\textbf{rí}etes,~*
		et colles, sic\textit{ut} \textit{a}\textit{gni} \textbf{ó}vium.
	
	 7. A fácie Dómini mo\textit{ta} \textit{est} \textbf{ter}ra,~*
		a fáci\textit{e} \textit{De}\textit{i} \textbf{Ja}cob.
	
	 8. Qui convértit petram in sta\textit{gna} \textit{a}\textbf{quá}rum,~*
		et rupem in \textit{fon}\textit{tes} \textit{a}\textbf{quá}rum.
	
	 9. Non nobis, Dómi\textit{ne}, \textit{non} \textbf{no}bis:~*
		sed nómini \textit{tu}\textit{o} \textit{da} \textbf{gló}riam.
	
	 10. Super misericórdia tua, et veri\textit{tá}\textit{te} \textbf{tu}a:~*
		nequándo dicant gentes: Ubi est \textit{De}\textit{us} \textit{e}\textbf{ó}rum?
	
	 11. Deus autem nos\textit{ter} \textit{in} \textbf{cæ}lo:~*
		ómnia quæcúmque \textit{vó}\textit{lu}\textit{it}, \textbf{fe}cit.
	
	 12. Simulácra géntium argén\textit{tum}, \textit{et} \textbf{au}rum,~*
		ópera \textit{má}\textit{nu}\textit{um} \textbf{hó}minum.
	
	 13. Os habent, et \textit{non} \textit{lo}\textbf{quén}tur:~*
		óculos habent, \textit{et} \textit{non} \textit{vi}\textbf{dé}bunt.
	
	 14. Aures habent, \textit{et} \textit{non} \textbf{áu}dient:~*
		nares habent, et \textit{non} \textit{o}\textit{do}\textbf{rá}bunt.
	
	 15. Manus habent, et non palpábunt:~\GreDagger\
		pedes habent, et non \textit{am}\textit{bu}\textbf{lá}bunt:~*
		non clamábunt in \textit{gút}\textit{tu}\textit{re} \textbf{su}o.
	
	 16. Símiles illis fiant qui fá\textit{ci}\textit{unt} \textbf{e}a:~*
		et omnes qui con\textit{fí}\textit{dunt} \textit{in} \textbf{e}is.
	
	 17. Domus Israël sperá\textit{vit} \textit{in} \textbf{Dó}mi\-no:~*
		adjútor eórum et pro\textit{téc}\textit{tor} \textit{e}\textbf{ó}rum est,
	
	 18. Domus Aaron sperá\textit{vit} \textit{in} \textbf{Dó}mi\-no:~*
		adjútor eórum et pro\textit{téc}\textit{tor} \textit{e}\textbf{ó}rum est,
	
	 19. Qui timent Dóminum, speravé\textit{runt} \textit{in} \textbf{Dó}mino:~*
		adjútor eórum et pro\textit{téc}\textit{tor} \textit{e}\textbf{ó}rum est.
	
	 20. Dóminus memor \textit{fu}\textit{it} \textbf{nos}tri:~*
		et be\textit{ne}\textit{dí}\textit{xit} \textbf{no}bis:
	
	 21. Benedíxit dó\textit{mu}\textit{i} \textbf{Is}raël:~*
		benedíxit \textit{dó}\textit{mu}\textit{i} \textbf{A}aron.
	
	 22. Benedíxit ómnibus, qui \textit{ti}\textit{ment} \textbf{Dó}minum,~*
		pusíl\textit{lis} \textit{cum} \textit{ma}\textbf{jó}ribus.
	
	 23. Adjíciat Dó\textit{mi}\textit{nus} \textbf{su}per vos:~*
		super vos, et super \textit{fí}\textit{li}\textit{os} \textbf{ves}tros.
	
	 24. Benedícti \textit{vos} \textit{a} \textbf{Dó}mino,~*
		qui fecit \textit{cæ}\textit{lum}, \textit{et} \textbf{ter}ram.
	
	 25. Cælum \textit{cæ}\textit{li} \textbf{Dó}mino:~*
		terram autem dedit \textit{fí}\textit{li}\textit{is} \textbf{hó}minum.
	
	 26. Non mórtui laudá\textit{bunt} \textit{te}, \textbf{Dó}mine:~*
		neque omnes, qui descén\textit{dunt} \textit{in} \textit{in}\textbf{fér}num.
		
	27. Sed nos qui vívimus, benedí\textit{ci}\textit{mus} \textbf{Dó}mino,~*
		ex hoc nunc et \textit{us}\textit{que} \textit{in} \textbf{s\'{\ae}}culum.
}{
	%\input{../psalms/english/ps113}
	2. Judea was made his sanctuary, Israel his dominion.

	3. The sea saw and fled: Jordan was turned back.
	
	4. The mountains skipped like rams, and the hills like the lambs of the flock.
	
	\pagebreak
	
	5. What ailed thee, O thou sea, that thou didst flee: and thou, O Jordan, that thou wast turned back?
	
	6. Ye mountains, that ye skipped like rams, and ye hills, like lambs of the flock?
	
	7. At the presence of the Lord the earth was moved, at the presence of the God of Jacob:
	
	8. Who turned the rock into pools of water, and the stony hill into fountains of waters.
	
	9. Not to us, O Lord, not to us; but to thy name give glory.
	
	10. For thy mercy, and for thy truth's sake: lest the gentiles should say: Where is their God?
	
	11. But our God is in heaven: he hath done all things whatsoever he would.
	
	12. The idols of the gentiles are silver and gold, the works of the hands of men.
	
	13. They have mouths and speak not: they have eyes and see not.
	
	14. They have ears and hear not: they have noses and smell not.
	
	15. They have hands and feel not: they have feet and walk not: neither shall they cry out through their throat.
	
	16. Let them that make them become like unto them: and all such as trust in them.
	
	17. The house of Israel hath hoped in the Lord: he is their helper and their protector.
	
	18. The house of Aaron hath hoped in the Lord: he is their helper and their protector.
	
	19. They that fear the Lord hath hoped in the Lord: he is their helper and their protector.
	
	\pagebreak
	
	20. The Lord hath been mindful of us, and hath blessed us.
	
	21. He hath blessed the house of Israel: he hath blessed the house of Aaron.
	
	22. He hath blessed all that fear the Lord, both little and great.
	
	23. May the Lord add blessings upon you: upon you, and upon your children.
	
	24. Blessed be you of the Lord, who made heaven and earth.
	
	25. The heaven of heaven is the Lord's: but the earth he has given to the children of men.
	
	26. The dead shall not praise thee, O Lord: nor any of them that go down to hell.
	
	27. But we that live bless the Lord: from this time now and for ever.
	
	Glory be.
}

\end{latinenglishsection}

 Glória Pa\textit{tri}, \textit{et} \textbf{Fí}lio,~*
	et Spi\textit{rí}\textit{tu}\textit{i} \textbf{Sanc}to.

 Sicut erat in princípio, et \textit{nunc}, \textit{et} \textbf{sem}per,~*
	et in s\'{\ae}cula sæ\textit{cu}\textit{ló}\textit{rum}. \textbf{A}men.

\gresetinitiallines{0}
\gregorioscore{ps113-antiphon}
\textit{\textnormal{Ant.} Behold, the great Prophet shall come; and He shall renew Jerusalem, alleluia.}

\section*{Little Chapter (Romans 13:11)}

\begin{latinenglishsection}

\latinenglish{
	
	Fratres: Hora est jam nos de somno súrgere:~\GreDagger\
	nunc enim própior est nostra salus,~*
	quam cum credídimus.
	\Rbar.~Deo grátias.
}{
	 Brethren: It is now the hour for us to rise from sleep:
	 for now our salvation is nearer than when we believed.
	 \Rbar.~Thanks be to God.
}
\end{latinenglishsection}

\section*{Hymn}

\gresetinitiallines{1}
\gregorioscore{../hymns/conditor-alme-siderum}

\begin{multicols}{2}

1. Creator of the stars of night,
Thy people's everlasting light,
Jesu, Redeemer, save us all,
and hear Thy servants when they call.

2. Thou, grieving that the ancient curse
should doom to death a universe,
hast found the medicine, full of grace,
to save and heal a ruined race.

3. Thou camest, the Bridegroom of the Bride,
as drew the world to evening tide,
proceeding from a virgin shrine,
the spotless Victim all divine.

4.  At whose dread Name, majestic now,
all knees must bend, all hearts must bow;
and things celestial Thee shall own,
and things terrestrial Lord alone.

5. O Thou whose coming is with dread,
to judge and doom the quick and dead,
preserve us, while we dwell below,
from every insult of the foe.

6. To God the Father, God the Son,
and God the Spirit, Three in One,
laud, honor, might, and glory be
from age to age eternally. Amen. 

\end{multicols}

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>V/</sp>. Ro(h)rá(h)te(h) cæ(h)li(h) dé(h)su(h)per,(h) et(h) nu(h)bes(h) plu(h)ant(h) jus(h)tum.(g'_/hvGF'E/fgf.) (::)
}

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>R/</sp>. A(h)pe(h)ri(h)á(h)tur(h) ter(h)ra,(h) et(h) gér(h)mi(h)net(h) Sal(h)va(h)tó(h)rem.(g'_/hvGF'E/fgf.) (::)
}

\textit{\Vbar.~Drop down dew, ye heavens, from above, and let the clouds rain the Just One.
\Rbar.~Let the earth be opened, and bud forth the Savior.}

\vfill

\section*{Magnificat}

\gresetinitiallines{1}
\gregorioscore{magnificat-intonation}

\input{../psalms/magnificat-8G}

\pagebreak

\gresetinitiallines{0}
\gregorioscore{magnificat-antiphon}

\textit{Fear not, Mary, for you have found grace with God. Behold, you shall conceive and give birth to a Son, alleluia.}

\section*{Conclusion}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~Dóminus vobíscum.\\
	\Rbar.~Et cum spíritu tuo.
	
	Orémus. Excita, qu\'{\ae}sumus, Dómine, poténtiam tuam, et veni:~\GreDagger\
	ut ab imminéntibus peccatórum nostrórum perículis, te mereámur protegénte éripi, te liberánte salvári.
	Qui vivis.
	\Rbar.~Amen.
	
	\rubric{One or more commemorations follow, depending on the day.}
}{
	The Lord be with you.
	\Rbar.~And with thy spirit.
	
	Let us pray.
	Show forth Thy power, O Lord, we beseech Thee, and come, that with Thee as our protector we may be rescued from the impending danger of our sins; and with Thee as our deliverer, we may obtain our salvation. Who liveth.
	\Rbar.~Amen.
}

\latinenglish{
	\Rbar.~Amen. \\
	\Vbar.~Dóminus vobíscum. \\
	\Rbar.~Et cum spíritu tuo.
}{
	\Rbar.~Amen. \Vbar.~The Lord be with you. \Rbar.~And with thy spirit.
	\Vbar.~Let us bless the Lord. \Rbar.~Thanks be to God.
}

\end{latinenglishsection}

\gresetinitiallines{0}
\gregorioscore{../common/benedicamus-advent-lent}

\begin{latinenglishsection}

\latinenglish{
	\Vbar. Fidélium ánimæ, per misericórdiam Dei, requiéscant in pace. \\
	\Rbar. Amen.
}{
	May the souls of the faithful departed, through the mercy of God, rest in peace. \Rbar.~Amen.
}

\latinenglish{
	Pater noster \textit{(silently)}.
}{
	Our Father\dots
}

\rubric{If no other service follows:}

\latinenglish{
	\Vbar. Dóminus det nobis suam pacem. \\
	\Rbar. Et vitam ætérnam. Amen.
}{
	May the Lord grant us his peace. \Rbar.~And life eternal. Amen.
}

\end{latinenglishsection}

\end{document}