\documentclass{../vespers-booklet}
\usepackage{multicol}

\title{In Festo Omnium Sanctorum\\Ad I. Vesperas}
\author{First Vespers of the Feast of All Saints}

\begin{document}

\chapter*{Dominica Ad Vesperas}

\textit{The following prayers are said silently before the Office:}

\begin{latinenglishsection}

\latinenglish{
	Aperi, + Dómine, os meum ad benedicéndum nomen sanctum tuum:
	+ munda quoque cor meum ab ómnibus vanis, pervérsis et aliénis cogitatiónibus;
	intelléctum illúmina, afféctum inflámma, ut digne, atténte ac devóte hoc Offícium recitáre váleam,
	et exaudíri mérear ante conspéctum divínæ Majestátis tuæ.
	Per Christum Dóminum nostrum. 
	Amen.
}{
	Open, + O Lord, my mouth to bless Thy holy Name; + cleanse also my heart from all vain, evil, and wandering thoughts; enlighten my understanding and kindle my affections; that I may worthily, attentively, and devoutly say this Office, and so merit to be heard before the presence of Thy divine Majesty.  Through Christ our Lord.  Amen.
}

\latinenglish{
	Domine, in unióne illíus divínæ intentiónis, qua ipse in terris laudes Deo persolvísti, hanc tibi Horam persólvo.
}{
	O Lord, in union with that divine intention wherewith Thou, whilst here on earth, didst render praises unto God, I desire to offer this Hour of prayer unto Thee.
}

\latinenglish{
	Pater. Ave.
}{}

 \end{latinenglishsection}
 
 \gresetinitiallines{1}
\gregorioscore{../common/deus-in-adjutorium}

\textit{
O God, come to my assistance.
\Vbar.~O Lord, make haste to help me.
Glory be to the Father, and to the Son, and to the Holy Spirit,
as it was in the beginning, is now, and ever shall be, world without end. Amen.
Alleluia.}

\section*{Psalm 109}

\textit{\textnormal{Ps.} The Lord said to my Lord: Sit thou at my right hand.}

\gresetinitiallines{1}
\gregorioscore{ps109-intonation}

%\input{../psalms/ps109-7}

 \begin{latinenglishsection}

\latinenglish{
	2. Donec ponam ini\textbf{mí}cos \textbf{tu}os,~*
		scabéllum \textbf{pe}dum tu\textbf{ó}rum.
	
	3. Virgam virtútis tuæ emíttet Dómi\textbf{nus} ex \textbf{Si}on:~*
		domináre in médio inimi\textbf{có}rum tu\textbf{ó}rum.
	
	4. Tecum princípium in die virtútis tuæ in splendóri\textbf{bus} sanc\textbf{tó}rum:~*
		ex útero ante lucíferum \textbf{gé}nu\textbf{i} te.
	
	5. Jurávit Dóminus, et non p{\oe}ni\textbf{té}bit \textbf{e}um:~*
		Tu es sacérdos in ætérnum secúndum órdi\textbf{nem} Mel\textbf{chí}sedech.
	
	6. Dóminus a \textbf{dex}tris \textbf{tu}is,~*
		confrégit in die iræ \textbf{su}æ \textbf{re}ges.
	
	7. Judicábit in natiónibus, im\textbf{plé}bit ru\textbf{í}nas:~*
		conquassábit cápita in \textbf{ter}ra mul\textbf{tó}rum.
	
	8. De torrénte in \textbf{vi}a \textbf{bi}bet:~*
		proptérea exal\textbf{tá}bit \textbf{ca}put.
	
	Glória \textbf{Pa}tri, et \textbf{Fí}lio,~*
		et Spi\textbf{rí}tui \textbf{Sanc}to.
}{
	1. The Lord said to my Lord: Sit thou at my right hand.
	\input{../psalms/english/ps109}
}

\end{latinenglishsection}

Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textbf{ló}rum. \textbf{A}men.
	
\gresetinitiallines{0}
\gregorioscore{ps109-antiphon}

\textit{\textnormal{Ant.} The Lord said to my Lord: Sit thou at my right hand.}

\section*{Psalm 110}

\textit{\textnormal{Ps.} I will praise thee, O Lord, with my whole heart; in the council of the just: and in the congregation.}

\gresetinitiallines{1}
\gregorioscore{ps110-intonation}

 \begin{latinenglishsection}

\latinenglish{
	2. Magna \textbf{ó}pera \textbf{Dó}\textbf{mi}ni:~*
		exquisíta in omnes volun\textbf{tá}tes \textbf{e}jus.
	
	3. Conféssio et magnificéntia \textbf{o}pus \textbf{e}jus:~*
		et justítia ejus manet in \textbf{s\'{\ae}}culum \textbf{s\'{\ae}}culi.
	
	4. Memóriam fecit mirabílium suórum,~\GreDagger\
		miséricors et mise\textbf{rá}tor \textbf{Dó}\textbf{mi}\-nus:~*
		escam dedit ti\textbf{mén}ti\textbf{bus} se.
	
	5. Memor erit in s\'{\ae}culum testa\textbf{mén}ti \textbf{su}i:~*
		virtútem óperum suórum annuntiábit \textbf{pó}pulo \textbf{su}o:
	
	6. Ut det illis heredi\textbf{tá}tem \textbf{gén}\textbf{ti}um: *
		ópera mánuum ejus véritas, \textbf{et} ju\textbf{dí}cium.
}{
	 2. Great are the works of the Lord: sought out according to all his wills.
	 
	 3. His work is praise and magnificence: and his justice continueth for ever and ever.
	 
	 4.  He hath made a remembrance of his wonderful works, being a merciful and gracious Lord: he hath given food to them that fear him. 	
	 
	 5. He will be mindful for ever of his covenant: he will shew forth to his people the power of his works.
	 
	 6. That he may give them the inheritance of the Gentiles: the works of his hands are truth and judgment.
}

\end{latinenglishsection}

\vfill
\pagebreak

\gresetinitiallines{0}
\gabcsnippet{
(c4) 7. Fi(i)dé(i)li(i)a(i) óm(i)ni(i)a(i) man(i)dá(i)ta(i) e(i)jus: †(h.) con(i)fir(i)má(i)ta(i) in(i) <b>s<sp>'ae</sp></b>(k)cu(j)lum(j) <b>s<sp>'ae</sp></b>(j)<b>cu</b>(ih)li,(j.) *(:) fac(i)ta(i) in(i) ve(i)ri(i)tá(i)te(i) et(i) <b>æ</b>(j)qui(h)<b>tá</b>(j)te.(i.) (::)
}

 \begin{latinenglishsection}

\latinenglish{
	
%	7. Fidélia ómnia mandáta ejus:~\GreDagger\
%		confirmáta in \textbf{s\'{\ae}}culum \textbf{s\'{\ae}}\textbf{cu}li,~*
%		facta in veritáte et \textbf{æ}qui\textbf{tá}te.
	
	8. Redemptiónem misit \textbf{pó}pulo \textbf{su}o:~*
		mandávit in ætérnum testa\textbf{mén}tum \textbf{su}um.
	
	9. Sanctum, et terríbile \textbf{no}men \textbf{e}jus:~*
		inítium sapiéntiæ \textbf{ti}mor \textbf{Dó}mini.
	
	10. Intelléctus bonus ómnibus faci\textbf{én}tibus \textbf{e}um:~*
		laudátio ejus manet in \textbf{s\'{\ae}}culum \textbf{s\'{\ae}}culi.
	
	Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~*
		et Spi\textbf{rí}tui \textbf{Sanc}to.
}{
	 
	 7. All his commandments are faithful: confirmed for ever and ever, made in truth and equity.
	 
	 8. He hath sent redemption to his people: he hath commanded his covenant for ever.
	 
	 9. Holy and terrible is his name: the fear of the Lord is the beginning of wisdom.
	 
	 10. A good understanding to all that do it: his praise continueth for ever and ever. 
	 
	Glory be.
}

\end{latinenglishsection}


Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textbf{ló}rum. \textbf{A}men.
	
\gresetinitiallines{0}
\gregorioscore{ps110-antiphon}

\textit{\textnormal{Ant.} Great are the works of the Lord: sought out according to all his wills.}

\vfill
\pagebreak

\section*{Psalm 111}

\textit{\textnormal{Ps.} Blessed is the man that feareth the Lord: he shall delight exceedingly in his commandments.}

\gresetinitiallines{1}
\gregorioscore{ps111-intonation}

%\input{../psalms/ps111-4g}

 \begin{latinenglishsection}

\latinenglish{
	2. Potens in terra erit \textit{se}\textit{men} \textbf{e}jus:~*
		generátio rectórum benedi\textbf{cé}tur.
	
	3. Glória, et divítiæ in \textit{do}\textit{mo} \textbf{e}jus:~*
		et justítia ejus manet in s\'{\ae}culum \textbf{s\'{\ae}}culi.
	
	4. Exórtum est in ténebris \textit{lu}\textit{men} \textbf{rec}tis:~*
		miséricors, et miserátor, et \textbf{jus}tus.
	
	5. Jucúndus homo qui miserétur et cómmodat,~\GreDagger\
		dispónet sermónes suos \textit{in} \textit{ju}\textbf{dí}cio:~*
		quia in ætérnum non commo\textbf{vé}bitur.
	
	6. In memória ætérna \textit{e}\textit{rit} \textbf{jus}tus:~*
		ab auditióne mala non ti\textbf{mé}bit.
	
	7. Parátum cor ejus speráre in Dómino,~\GreDagger\
		confirmátum \textit{est} \textit{cor} \textbf{e}jus:~*
		non commovébitur donec despíciat inimícos \textbf{su}os.
	
	8. Dispérsit, dedit paupéribus:~\GreDagger\
		justítia ejus manet in s\'{\ae}\textit{cu}\textit{lum} \textbf{s\'{\ae}}cu\-li,~*
		cornu ejus exaltábitur in \textbf{gló}ria.
}{
	2. His seed shall be mighty upon earth: the generation of the righteous shall be blessed.
	
	3. Glory and wealth shall be in his house: and his justice remaineth for ever and ever.
	
	4. To the righteous a light is risen up in darkness: he is merciful, and compassionate and just.
	
	5. Acceptable is the man that sheweth mercy and lendeth: he shall order his words with judgment:
	because he shall not be moved for ever.
	
	6. The just shall be in everlasting remembrance: he shall not fear the evil hearing.
	
	7. His heart is ready to hope in the Lord: his heart is strengthened, he shall not be moved until he look over his enemies.
	
	8. He hath distributed, he hath given to the poor: his justice remaineth for ever and ever: his horn shall be exalted in glory.
}

\end{latinenglishsection}

\vfill
\pagebreak

\gresetinitiallines{0}
\gabcsnippet{
(c4) 9. Pec(h)cá(h)tor(h) vi(h)dé(h)bit,(h) et(h) i(h)ra(h)scé(h)tur, +(g.) dén(h)ti(h)bus(h) su(h)is(h) fre(h)met(h) <i>et</i>(g) <i>ta</i>(h)<b>bé</b>(i)scet:(h.) *(:) de(h)si(h)dé(h)ri(h)um(h) pec(h)ca(h)tó(h)rum(h) per(h)<b>í</b>(h)bit.(g.) (::)
}

 \begin{latinenglishsection}

\latinenglish{	
%	9. Peccátor vidébit, et irascétur,~\GreDagger\
%		déntibus suis fremet \textit{et} \textit{ta}\textbf{bé}scet:~*
%		desidérium peccatórum per\textbf{í}bit.
	
	Glória Pa\textit{tri}, \textit{et} \textbf{Fí}lio,~*
		et Spirítui \textbf{Sanc}to.
	
	Sicut erat in princípio, et \textit{nunc}, \textit{et} \textbf{sem}per,~*
		et in s\'{\ae}cula sæculórum. \textbf{A}men.
}{	
	9. The wicked shall see, and shall be angry, he shall gnash with his teeth and pine away: the desire of the wicked shall perish. 
	
	Glory be.
}

\end{latinenglishsection}
	
\gresetinitiallines{0}
\gregorioscore{ps111-antiphon}

\textit{\textnormal{Ant.} He that feareth the Lord, shall delight exceedingly in his commandments.}

\section*{Psalm 112}

\textit{\textnormal{Ps.} Praise the Lord, ye children: praise ye the name of the Lord.}

\gresetinitiallines{1}
\gregorioscore{ps112-intonation}

%\input{../psalms/ps112-7}

 \begin{latinenglishsection}

\latinenglish{
	 2. Sit nomen Dómini \textbf{be}ne\textbf{díc}tum,~*
		ex hoc nunc, et \textbf{us}que in \textbf{s\'{\ae}}culum.
	
	 3. A solis ortu usque \textbf{ad} oc\textbf{cá}sum,~*
		laudábile \textbf{no}men \textbf{Dó}mini.
	
	 4. Excélsus super omnes \textbf{gen}tes \textbf{Dó}\-minus,~*
		et super cælos \textbf{gló}ria \textbf{e}jus.
	
	 5. Quis sicut Dóminus, Deus noster, qui in \textbf{al}tis \textbf{há}bitat,~*
		et humília réspicit in cælo \textbf{et} in \textbf{ter}ra?
	
	 6. Súscitans a \textbf{ter}ra \textbf{ín}opem,~*
		et de stércore \textbf{é}rigens \textbf{páu}perem:
	
	 7. Ut cóllocet eum \textbf{cum} prin\textbf{cí}pi\-bus,~*
		cum princípibus \textbf{pó}puli \textbf{su}i.
	
	 8. Qui habitáre facit stéri\textbf{lem} in \textbf{do}\-mo,~*
		matrem fili\textbf{ó}rum læ\textbf{tán}tem.
		
	Glória \textbf{Pa}tri, et \textbf{Fí}lio,~*
		et Spi\textbf{rí}tui \textbf{Sanc}to.

}{
	\input{../psalms/english/ps112}
}

\end{latinenglishsection}
		
 Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textbf{ló}rum. \textbf{A}men.
	
\gresetinitiallines{0}
\gregorioscore{ps112-antiphon}

\textit{\textnormal{Ant.} Blessed be the name of the Lord for ever.}

\section*{Psalm 113}

\textit{\textnormal{Ps.} When Israel went out of Egypt, the house of Jacob from a barbarous people.}

\gresetinitiallines{1}
\gregorioscore{ps113-intonation-no-flex}

%\input{../psalms/ps113-per}

 \begin{latinenglishsection}

\latinenglish{
	2. Facta est Jud\'{\ae}a sanctifi\textit{cá}\textit{ti}\textit{o} \textbf{e}jus,~*
		Israël potés\textit{tas} \textbf{e}jus.
	
	3. Mare \textit{vi}\textit{dit}, \textit{et} \textbf{fu}git:~*
		Jordánis convérsus est \textit{re}\textbf{trór}sum.
	
	4. Montes exsultavé\textit{runt} \textit{ut} \textit{a}\textbf{rí}etes,~*
		et colles sicut a\textit{gni} \textbf{ó}vium.
}{
	2. Judea was made his sanctuary, Israel his dominion.
	
	3. The sea saw and fled: Jordan was turned back.
	
	4. The mountains skipped like rams, and the hills like the lambs of the flock.
}

\end{latinenglishsection}

\vfill
\pagebreak

\gresetinitiallines{0}
\gabcsnippet{
	(c4) 5. Quid(h) est(h) ti(h)bi,(h) ma(h)<i>re</i>,(g) <i>quod</i>(ixi) <i>fu</i>(h)<b>gís</b>(g)ti:(f.) *(:)
	et(g) tu,(g) Jor(g)dá(g)nis,(g) qui(g)a(g) con(g)vér(g)sus(g) es(g) <i>re</i>(d)<b>trór</b>(f)sum?(ed..)
	<i>Flex:</i>(::)  pal(h)pá(h)bunt: †(g. h h h  ::)
}

 \begin{latinenglishsection}

\latinenglish{	
%	5. Quid est tibi, ma\textit{re}, \textit{quod} \textit{fu}\textbf{gís}ti:~*
%		et tu, Jordánis, quia convérsus es \textit{re}\textbf{trór}sum?
	
	6. Montes, exsultástis \textit{sic}\textit{ut} \textit{a}\textbf{rí}etes,~*
		et colles, sicut a\textit{gni} \textbf{ó}vium.
	
	7. A fácie Dómini \textit{mo}\textit{ta} \textit{est} \textbf{ter}ra,~*
		a fácie De\textit{i} \textbf{Ja}cob.
	
	8. Qui convértit petram in \textit{sta}\textit{gna} \textit{a}\textbf{quá}rum,~*
		et rupem in fontes \textit{a}\textbf{quá}\-rum.
	
	9. Non nobis, Dó\textit{mi}\textit{ne}, \textit{non} \textbf{no}bis:~*
		sed nómini tuo \textit{da} \textbf{gló}riam.
	
	10. Super misericórdia tua, et ve\textit{ri}\textit{tá}\textit{te} \textbf{tu}a:~*
		nequándo dicant gentes: Ubi est Deus \textit{e}\textbf{ó}rum?
	
	11. Deus autem \textit{nos}\textit{ter} \textit{in} \textbf{cæ}lo:~*
		ómnia quæcúmque vólu\textit{it}, \textbf{fe}cit.
	
	12. Simulácra géntium ar\textit{gén}\textit{tum}, \textit{et} \textbf{au}rum,~*
		ópera mánu\textit{um} \textbf{hó}minum.
	
	13. Os habent, \textit{et} \textit{non} \textit{lo}\textbf{quén}tur:~*
		óculos habent, et non \textit{vi}\textbf{dé}bunt.
	
	14. Aures ha\textit{bent}, \textit{et} \textit{non} \textbf{áu}dient:~*
		nares habent, et non o\textit{do}\textbf{rá}bunt.
	
	15. Manus habent, et non palpábunt:~\GreDagger\
		pedes habent, et \textit{non} \textit{am}\textit{bu}\textbf{lá}\-bunt:~*
		non clamábunt in gúttu\textit{re} \textbf{su}o.
	
	16. Símiles illis fiant qui \textit{fá}\textit{ci}\textit{unt} \textbf{e}a:~*
		et omnes qui confídunt \textit{in} \textbf{e}is.
	
	17. Domus Israël spe\textit{rá}\textit{vit} \textit{in} \textbf{Dó}mi\-no:~*
		adjútor eórum et protéctor \textit{e}\textbf{ó}rum est,
	
	18. Domus Aaron spe\textit{rá}\textit{vit} \textit{in} \textbf{Dó}mi\-no:~*
		adjútor eórum et protéctor \textit{e}\textbf{ó}rum est,
	
	19. Qui timent Dóminum, spera\textit{vé}\textit{runt} \textit{in} \textbf{Dó}mino:~*
		adjútor eórum et protéctor \textit{e}\textbf{ó}rum est.
	
	20. Dóminus me\textit{mor} \textit{fu}\textit{it} \textbf{nos}tri:~*
		et benedí\textit{xit} \textbf{no}bis:
	
	21. Benedíxit \textit{dó}\textit{mu}\textit{i} \textbf{Is}raël:~*
		benedíxit dómu\textit{i} \textbf{A}aron.
	
	22. Benedíxit ómnibus, \textit{qui} \textit{ti}\textit{ment} \textbf{Dó}minum,~*
		pusíllis cum \textit{ma}\textbf{jó}ribus.
	
	23. Adjíciat \textit{Dó}\textit{mi}\textit{nus} \textbf{su}per vos:~*
		super vos, et super fíli\textit{os} \textbf{ves}tros.
	
	24. Benedíc\textit{ti} \textit{vos} \textit{a} \textbf{Dó}mino,~*
		qui fecit cælum, \textit{et} \textbf{ter}ram.
	
	25. Cæ\textit{lum} \textit{cæ}\textit{li} \textbf{Dó}mino:~*
		terram autem dedit fíli\textit{is} \textbf{hó}minum.
	
	26. Non mórtui lau\textit{dá}\textit{bunt} \textit{te}, \textbf{Dó}mine:~*
		neque omnes, qui descéndunt in \textit{in}\textbf{fér}\-num.
	
	27. Sed nos qui vívimus, bene\textit{dí}\textit{ci}\textit{mus} \textbf{Dó}mino,~*
		ex hoc nunc et usque \textit{in} \textbf{s\'{\ae}}culum.
	

}{	
	5. What ailed thee, O thou sea, that thou didst flee: and thou, O Jordan, that thou wast turned back?
	
	6. Ye mountains, that ye skipped like rams, and ye hills, like lambs of the flock?
	
	7. At the presence of the Lord the earth was moved, at the presence of the God of Jacob:
	
	8. Who turned the rock into pools of water, and the stony hill into fountains of waters.
	
	9. Not to us, O Lord, not to us; but to thy name give glory.
	
	10. For thy mercy, and for thy truth's sake: lest the gentiles should say: Where is their God?
	
	11. But our God is in heaven: he hath done all things whatsoever he would.
	
	12. The idols of the gentiles are silver and gold, the works of the hands of men.
	
	13. They have mouths and speak not: they have eyes and see not.
	
	14. They have ears and hear not: they have noses and smell not.
	
	15. They have hands and feel not: they have feet and walk not: neither shall they cry out through their throat.
	
	16. Let them that make them become like unto them: and all such as trust in them.
	
	17. The house of Israel hath hoped in the Lord: he is their helper and their protector.
	
	18. The house of Aaron hath hoped in the Lord: he is their helper and their protector.
	
	19. They that fear the Lord hath hoped in the Lord: he is their helper and their protector.
	
	20. The Lord hath been mindful of us, and hath blessed us.
	
	21. He hath blessed the house of Israel: he hath blessed the house of Aaron.
	
	22. He hath blessed all that fear the Lord, both little and great.
	
	23. May the Lord add blessings upon you: upon you, and upon your children.
	
	24. Blessed be you of the Lord, who made heaven and earth.
	
	25. The heaven of heaven is the Lord's: but the earth he has given to the children of men.
	
	26. The dead shall not praise thee, O Lord: nor any of them that go down to hell.
	
	27. But we that live bless the Lord: from this time now and for ever.
	
	Glory be.
}

\end{latinenglishsection}

Glória \textit{Pa}\textit{tri}, \textit{et} \textbf{Fí}lio,~*
	et Spirítu\textit{i} \textbf{Sanc}to.

Sicut erat in princípio, \textit{et} \textit{nunc}, \textit{et} \textbf{sem}per,~*
	et in s\'{\ae}cula sæculó\textit{rum}. \textbf{A}men.
	
\gresetinitiallines{0}
\gregorioscore{ps113-antiphon}

\textit{\textnormal{Ant.} But our God is in heaven: he hath done all things whatsoever he could.}

\vfill
\pagebreak

\section*{Little Chapter (2 Cor. 1:3-4)}

\begin{latinenglishsection}

\latinenglish{
	Benedíctus Deus, et Pater Dómini nostri Jesu Christi,~\GreDagger\
	Pater misericordiárum, et Deus totíus consolatiónis,~*
	qui consolátur nos in omni tribulatióne nostra.
	\Rbar.~Deo grátias.
}{
	Blessed be the God and Father of our Lord Jesus Christ,
	the Father of mercies, and the God of all comfort,
	Who comforteth us in all our tribulation. 
	 \Rbar.~Thanks be to God.
}

\end{latinenglishsection}

\section*{Hymn}

\gresetinitiallines{1}
\gregorioscore{../hymns/lucis-creator-optime}

{\itshape
1. O blest Creator of the light,
Who mak'st the day with radiance bright,
and o'er the forming world didst call
the light from chaos first of all;

2. Whose wisdom joined in meet array
the morn and eve, and named them Day:
night comes with all its darkling fears;
regard Thy people's prayers and tears.

3. Lest, sunk in sin, and whelmed with strife,
they lose the gift of endless life;
while thinking but the thoughts of time,
they weave new chains of woe and crime. 

4. But grant them grace that they may strain
the heavenly gate and prize to gain:
each harmful lure aside to cast,
and purge away each error past.

5. O Father, that we ask be done,
through Jesus Christ, Thine only Son;
Who, with the Holy Ghost and Thee,
doth live and reign eternally. Amen. 
}

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>V/</sp>. Di(h)ri(h)gá(h)tur(h) Dó(h)mi(h)ne(h) o(h)rá(h)ti(h)o(h) me(h)a.(g/hvGF'E/fgf.) (::)
}

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>R/</sp>. Si(h)cut(h) in(h)cén(h)sum(h) in(h) con(h)spéc(h)tu(h) tu(h)o.(g/hvGF'E/fgf.) (::)
}

\textit{\Vbar.~Let my prayer be directed, O Lord.
\Rbar.~As incense in Thy sight.}

\vfill
\pagebreak

\section*{Magnificat}

\begin{rubricbox}

The antiphon at the \textit{Magnificat} and the prayer and commemorations which follow are different for each Sunday
and can be found in the accompanying insert or inserts.

\end{rubricbox}

\section*{Conclusion}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~Dóminus vobíscum. \\
	\Rbar.~Et cum spíritu tuo.
}{
	\Vbar.~The Lord be with you. \Rbar.~And with thy spirit.
	\Vbar.~Let us bless the Lord. \Rbar.~Thanks be to God.
}

\end{latinenglishsection}

\gresetinitiallines{0}
\gregorioscore{../common/benedicamus-sunday}
\begin{latinenglishsection}

\latinenglish{
	\Vbar. Fidélium ánimæ, per misericórdiam Dei, requiéscant in pace. \\
	\Rbar. Amen.
}{
	May the souls of the faithful departed, through the mercy of God, rest in peace. \Rbar.~Amen.
}

\latinenglish{
	Pater noster \textit{(silently)}.
}{
	Our Father\dots
}

\rubric{If no other service follows:}

\latinenglish{
	\Vbar. Dóminus det nobis suam pacem. \\
	\Rbar. Et vitam ætérnam. Amen.
}{
	May the Lord grant us his peace. \Rbar.~And life eternal. Amen.
}

\rubric{And the seasonal Marian anthem follows.}

\end{latinenglishsection}

\end{document}