\documentclass{../vespers-booklet}
\usepackage{multicol}

\begin{document}

\chapter*{First Vespers of Christ the King\\Insert for 30 Oct. 2021}

\gresetinitiallines{0}
\gabcsnippet{
	(c3) <sp>V/</sp>. Da(h)ta(h) est(h) mi(hi)hi(h_') (,) om(h)nis(f) po(e)tés(f_h)tas.(hiH'Ghih.ghG'FE'fggf.) (::)
}
	
\gresetinitiallines{0}
\gabcsnippet{
	(c3) <sp>R/</sp>. In(h) cæ(hi)lo(h_') (,) et(f') in(e) ter(f_h)ra.(hiH'Ghih.ghG'FE'fggf.) (::)
}

\textit{\Vbar.~All power has been given to Me.
\Rbar.~In heaven and on earth.}

\section*{Magnificat}

\textit{\textnormal{Ant Magn.} The Lord God shall give unto him the throne of David His father;
and He shall reign in the house of Jacob for ever, and of His Kingdom there shall be no end, alleluia.
\textnormal{Cant.} My soul doth magnify the Lord: and my spirit hath rejoiced in God my Saviour.
}

\begin{rubricbox}

After the leader intones up to the asterisk, \textbf{sit} and join in singing.

\end{rubricbox}

\gresetinitiallines{1}
\gregorioscore{magnificat-1v-antiphon-alone}

\begin{rubricbox}

\textbf{Stand} and make the sign of the cross with the cantor.

\end{rubricbox}

\gresetinitiallines{0}
\gregorioscore{magnificat-1v-cant-intonation}

 \begin{latinenglishsection}

\latinenglish{	
	3. Quia respéxit humilitátem an\textbf{cíl}læ \textbf{su}æ:~*
		ecce enim ex hoc beátam me dicent omnes gene\textit{ra}\textit{ti}\textbf{ó}nes.
	
	4. Quia fecit mihi \textbf{ma}gna qui \textbf{pot}ens est:~*
		et sanctum \textit{no}\textit{men} \textbf{e}jus.
	
	5. Et misericórdia ejus a progénie \textbf{in} pro\textbf{gé}nies~*
		timén\textit{ti}\textit{bus} \textbf{e}um.
	
	6. Fecit poténtiam in \textbf{brá}chio \textbf{su}o:~*
		dispérsit supérbos mente \textit{cor}\textit{dis} \textbf{su}i.
	
	7. Depósuit pot\textbf{én}tes de \textbf{se}de,~*
		et exal\textit{tá}\textit{vit} \textbf{hú}miles.
	
	8. Esuriéntes im\textbf{plé}vit \textbf{bo}nis:~*
		et dívites dimí\textit{sit} \textit{in}\textbf{á}nes.
	
	9. Suscépit Israël \textbf{pú}erum \textbf{su}um,~*
		recordátus misericór\textit{di}\textit{æ} \textbf{su}æ.
	
	10. Sicut locútus est ad \textbf{pa}tres \textbf{nos}tros,~*
		Abraham et sémini e\textit{jus} \textit{in} \textbf{s\'{\ae}}cula.
	
	\textit{(bow)} Glória \textbf{Pa}tri, et \textbf{Fí}lio,~*
		et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.

}{	
	\input{../psalms/english/magnificat}
}

\end{latinenglishsection}

	
\textit{(rise)} Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~*
	et in s\'{\ae}cula sæcu\textit{ló}\textit{rum}. \textbf{A}men.

\begin{rubricbox}

\textbf{Sit} and repeat the antiphon (starts on the first page): \textit{Dabit illi\dots},
then \textbf{stand}.

\end{rubricbox}

\section*{Collect}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~Dóminus vobíscum.\\
	\Rbar.~Et cum spíritu tuo.
	
	Orémus. Omnípotens sempitérne Deus, qui in dilécto Fílio tuo, universórum Rege, ómnia instauráre voluísti:
	concéde propítius; ut cunctæ famíliæ Géntium, peccáti vúlnere disgregátæ,
	ejus suavíssimo subdántur império. Qui tecum.
	\Rbar.~Amen.
}{
	The Lord be with you.
	\Rbar.~And with thy spirit.
	
	Let us pray.
	Almighty and everlasting God, who in Thy beloved Son, King of the whole world, hast willed to restore all things anew;
	grant in Thy mercy that all the families of nations, rent asunder by the wound of sin,
	may be subjected to His most gentle rule. Who with Thee liveth.
	\Rbar.~Amen.
}

\end{latinenglishsection}

\section*{Commemoration of the Sunday}

%% First of November, 23rd after Pentecost

%% TODO correct translation
\textit{\textnormal{Ant.} Holy Angels, our Guardians, defend us in battle, that we may not perish in the terrible judgment.}

\begin{rubricbox}

After the cantor intones up to the asterisk, \textbf{sit} and join in singing.

\end{rubricbox}

\gresetinitiallines{1}
\gregorioscore{../commemorations/sat-nov-1}

\begin{rubricbox}

\textbf{Stand.}

\end{rubricbox}

\begin{latinenglishsection}

\latinenglish{
	\Vbar.~Vespertína orátio ascéndat ad te Dómine.\\
	\Rbar.~Et descéndat super nos misericórdia tua.
	
	%% TODO correct prayer and translation
	Orémus.
	Deus, qui ineffábili providéntia sanctos Angelos tuos ad nostram custódiam míttere dignáris:
largíre supplícibus tuis; et eórum semper protectióne deféndi, et ætérna societáte gaudére.
}{
	May our evening prayer ascend to Thee, O Lord.
	\Rbar.~And may Thy mercy descend upon us.
	
	Let us pray.
	O God, Who in Thine ineffable providence hast deigned to send Thy holy Angels to watch over us,
	grant to Thy suppliants always to find safety in their protection and in eternity to share their happiness.
}

\end{latinenglishsection}

\begin{latinenglishsection}

\latinenglish{
	\Rbar.~Amen. \\
	\Vbar.~Dóminus vobíscum. \\
	\Rbar.~Et cum spíritu tuo.
}{
	\Rbar.~Amen. \Vbar.~The Lord be with you. \Rbar.~And with thy spirit.
	\Vbar.~Let us bless the Lord. \Rbar.~Thanks be to God.
}

\end{latinenglishsection}

\gresetinitiallines{1}
\gregorioscore{../common/benedicamus-1v-solem}

\begin{latinenglishsection}

\latinenglish{
	\Vbar. Fidélium ánimæ, per misericórdiam Dei, requiéscant in pace. \\
	\Rbar. Amen.
}{
	May the souls of the faithful departed, through the mercy of God, rest in peace. \Rbar.~Amen.
}

\latinenglish{
	Pater noster \textit{(silently)}.
}{
	Our Father\dots
}

\rubric{If no other service follows:}

\latinenglish{
	\Vbar. Dóminus det nobis suam pacem. \\
	\Rbar. Et vitam ætérnam. Amen.
}{
	May the Lord grant us his peace. \Rbar.~And life eternal. Amen.
}

\end{latinenglishsection}

\textit{The Marian anthem \textnormal{Salve Regina} follows (no. 224 in the \textnormal{Traditional Roman Hymnal}).}

\end{document}