\documentclass{../vespers-booklet}
\usepackage{multicol}

\begin{document}

\chapter*{Second Vespers of Christ the King}

\vfill
 
 \gresetinitiallines{1}
\gregorioscore{../common/deus-in-adjutorium-solemn}

\textit{
O God, come to my assistance.
\Vbar.~O Lord, make haste to help me.
Glory be to the Father, and to the Son, and to the Holy Spirit,
as it was in the beginning, is now, and ever shall be, world without end. Amen.
Alleluia.}

\pagebreak

\section*{Psalm 109}

\textit{\textnormal{Ant. 1.} He shalled be called the peaceful One, and His throne shall be established for ever.
 \textnormal{Ps.} The Lord said to my Lord: Sit thou at my right hand.}

\gresetinitiallines{1}
\gregorioscore{ps109-antiphon}

\input{../psalms/ps109-8G}

\textit{And the antiphon is repeated: \textnormal{Pacificus\dots}.}

\section*{Psalm 110}

\textit{\textnormal{Ant. 2.} His kingdom is a kingdom of all ages, and all kings shall serve and obey Him.
 \textnormal{Ps.} I will praise thee, O Lord, with my whole heart; in the council of the just: and in the congregation.}

\gresetinitiallines{1}
\gregorioscore{ps110-antiphon}

\input{../psalms/ps110-8c}

\textit{And the antiphon is repeated: \textnormal{Regnum ejus\dots}.}

\section*{Psalm 111}

\textit{\textnormal{Ant. 3.} Behold a Man, the Orient is His name; He shall sit and rule, and shall speak peace unto the nations.
 \textnormal{Ps.} Blessed is the man that feareth the Lord: he shall delight exceedingly in his commandments.}

\gresetinitiallines{1}
\gregorioscore{ps111-antiphon}

\input{../psalms/ps111-7a}

\textit{And the antiphon is repeated: \textnormal{Ecce vir Oriens\dots}.}

\section*{Psalm 112}

\textit{\textnormal{Ant. 4.} The Lord is our Judge, the Lord is our Law-giver; the Lord is our King, he will save us.
 \textnormal{Ps.} Blessed is the man that feareth the Lord: he shall delight exceedingly in his commandments.}

\gresetinitiallines{1}
\gregorioscore{ps112-antiphon}

\input{../psalms/ps112-3a}

\textit{And the antiphon is repeated: \textnormal{Dominus\dots}.}

\section*{Psalm 116}

\textit{\textnormal{Ant. 5.} Behold I have given thee for a light of the nations, that thou mayest be My salvation unto the ends of the earth.
 \textnormal{Ps.} O praise the Lord, all ye nations: praise him, all ye people.}

\gresetinitiallines{1}
\gregorioscore{ps116-antiphon}

\input{../psalms/ps116-8G}

\textit{And the antiphon is repeated: \textnormal{Ecce dedi te\dots}.}

\section*{Little Chapter (Col. 1:12-13)}

\begin{latinenglishsection}

\latinenglish{
	
	Fratres: Grátias ágimus Deo Patri, qui dignos nos fecit in partem sortis sanctórum in lúmine: \GreDagger\
	qui erípuit nos de potestáte tenebrárum, *
	et tránstulit in regnum Fílii dilectiónis suæ.
	\Rbar.~Deo grátias.
}{
	 Brethren: We give thanks to God the Father, who hath made us worthy to be partakers of the lot of the saints in light:
	 who hath delivered us from the power of darkness, and hath translated us into the kingdom of the Son of his love.
	 \Rbar.~Thanks be to God.
}

\section*{Magnificat}

\textit{\textnormal{Ant Magn.} He hath on His garment and on His thigh written: King of kings and Lord of lords. To Him be glory and empire for ever and ever. \textnormal{Cant.} My soul doth magnify the Lord: and my spirit hath rejoiced in God my Saviour.}

\gresetinitiallines{1}
\gregorioscore{magnificat-antiphon}

\input{../psalms/magnificat-7a}

\textit{And the antiphon is repeated: \textnormal{Habet in vestimento\dots}.}

\end{document}